### 2020-06-04 plots/pareto.tex
plots update

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={4e00da13-c81a-470c-a3b8-db36919bcc4d}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={17424e8b-9d66-41d4-9342-6596addcfe97}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={919a0304-361e-43fb-8e22-2dd0aa37e393}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={8a503cae-0298-4a7f-9779-9cdbb9c372ab}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={bf5fbc96-bfd6-4b9c-b7c4-ae90124f2ed9}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={1194bc33-0414-403c-af71-4325d2088744}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={349954f1-76cd-4bca-8826-e8c5478cb8f6}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={6f792b56-8565-4a9c-a0b1-e1b34a960cf1}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={1f1b30b7-99b6-4839-b4db-6b81b5c207a6}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={983c27c4-9507-442e-832b-e279e315fb14}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={0a7d34a8-6b04-46e4-b7a2-2c8a7956881d}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={3724c949-7487-474b-a429-7a1c21964e1f}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={a7b35447-2ba9-4fe1-be36-40d73f215c37}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7eeeb8c6-938a-4e4e-9520-d0fc3dae8e83}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={d678c89e-2af9-43ff-a744-cae1280ce438}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={25f20392-b69f-49bd-a635-0be03c74c855}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={68d53f2f-7b24-4ac4-b8a2-c2ec04d25fe9}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={4a827bf3-4301-46d5-8b87-27d268d54885}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={3b8108b1-72e4-46dd-9625-3954f74836c5}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={98b1028a-bf3d-423a-ba40-eda339d793e0}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

>>>>

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={e3f051b4-a68e-486f-b608-6a13dc46bdb0}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={ef39af70-0a29-4a15-8e65-bca546ca9489}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={8a5e683d-9b46-406e-a65b-a3ed6d04efe6}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7779a9b0-66f9-4007-96f4-e6d2ec265c78}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={3b6a467a-a7d8-40ea-8aae-58982e4c7813}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={514f4e34-2ec4-404f-bee4-1e7a5c8c498c}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={03945ca4-8958-4986-865f-d38ba070b814}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={0254ada2-8a05-4689-957e-8d313f86842e}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7be7d6c0-d826-4b63-85c8-4a37a5605e4a}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={526a97fb-2f22-43d3-b7f0-3f08966037a5}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={605dd1b6-3f1f-4def-9001-5889c2aae37a}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={0681bacc-1cbd-445a-b429-713421b04a3e}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={8ca4234d-2529-43fa-b313-caba4a4b1641}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={c6756010-4794-44a7-a667-e80dd9f7fbf9}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={305430f0-f2b7-45bc-a66e-638719c98bcd}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={49d3470e-a697-49bc-b9f1-e8f2595862d3}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={bd4058bd-1bb7-4bcd-9b9c-64e487eca27b}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={a1423905-57ce-45da-ad9e-17ca96b4b8bf}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={44f25ebe-f0eb-4342-beb6-60ddae64c4a9}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={a509524e-d232-4fc8-bcdb-3b60f960fed8}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

### 2020-06-04 plots/pareto_sir.tex
plots update

    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={c6416611-1574-49a0-9ea4-91e50a33118b}, draw opacity={0.25}, line width={0}, solid, mark={*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]

@@

    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={0b6b36d8-c846-4873-8ad0-9609ab2cf7aa}, draw opacity={0.25}, line width={0}, solid, mark={pentagon*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]

@@

    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={32500e26-f355-48fb-b27a-d77c0e6f6f11}, draw opacity={0.25}, line width={0}, solid, mark={diamond*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]

@@

    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={17fa3149-1072-43c8-8c21-8a953ad9b789}, draw opacity={1.0}, line width={2}, dashed]

@@

    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={92814b74-5dc8-4049-b104-86ec2005b545}, draw opacity={1.0}, line width={2}, solid]

@@

    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={01e229a2-0f53-4a30-b602-5c368ec01212}, draw opacity={1.0}, line width={2}, dashdotted]

@@

    \addlegendentry {NPU (real)}

@@

    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={2c7c1a19-783e-45b8-ba0c-5f0d47ee61d7}, draw opacity={0.8}, line width={4}, solid]

@@

    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={1bd494f5-4860-4f91-bdd7-b6e623424164}, draw opacity={0.8}, line width={4}, solid, forget plot]

@@

    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={99fd42b1-24fe-476a-9976-bd874af9786a}, draw opacity={0.8}, line width={4}, solid, forget plot]

@@

    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={78950b23-4587-48e7-ac69-7a173b42d7ff}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={55448a83-940d-42d2-bfa5-a69e99f44840}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={7029124d-f96e-4c96-8ccc-df7e7adb01de}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]

>>>>

    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={089ee56b-6822-4377-827c-374155ed22b5}, draw opacity={0.25}, line width={0}, solid, mark={*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]

@@

    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={fb8ade92-3de5-4181-955a-9068086f05cd}, draw opacity={0.25}, line width={0}, solid, mark={pentagon*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]

@@

    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={a4a2407a-9d13-4d5f-9806-f4dc789913ff}, draw opacity={0.25}, line width={0}, solid, mark={diamond*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]

@@

    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={6fca2f50-6519-44f2-b9d9-640264e75dcd}, draw opacity={1.0}, line width={2}, dashed]

@@

    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={4df2801f-27fe-4ea1-9f00-dbdbe35d4500}, draw opacity={1.0}, line width={2}, solid]

@@

    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={23f3a274-9dd0-40ba-b4c3-9bf7970f58c1}, draw opacity={1.0}, line width={2}, dashdotted]

@@

    \addlegendentry {RealNPU}

@@

    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={4d2d32cf-0078-477b-aca5-ac47612e3b35}, draw opacity={0.8}, line width={4}, solid]

@@

    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={b32b3689-d920-4aa7-9895-f3013f9b1a1b}, draw opacity={0.8}, line width={4}, solid, forget plot]

@@

    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={d04156b5-29d1-4f76-8661-f226866e6ee2}, draw opacity={0.8}, line width={4}, solid, forget plot]

@@

    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={daf90f21-20cf-4381-9c0f-30de95c3d54b}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={d719ac49-0b45-4546-885d-0971ecba6177}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={209e1cdb-c150-414a-bfc5-63b07ba91f51}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]
